The Morality of Arbitrage

### 2017-06-25 Slides/mercatus-slides.Rmd
Updating for Mercatus presentation.

>- It is apparent to me that the standard ethical arguments for capitalism are not having any purchase in the minds of most people.
>- Capitalism is presented as some kind of Faustian bargain: we like it for its wealth production and efficiency, but at bottom it is really about greed. It is rapacious and immoral.
>- It is readily apparent that many of our colleagues in the business disciplines believe this notion
>- __I'm afraid that our students do too!__ They leave the business school with some good technical tools, but not with an appreciation of just how much good they will do in their careers. 
>- That is on us! That's a failure on our part to teach correct principles.

@@

@@

<center>
<img src="images/xkcd.png" width=600 height=490 />
</center>

>>>>

>- It is apparent to me that the standard ethical arguments for capitalism are not having much purchase in the minds of most people.
>- Capitalism is presented as some kind of Faustian bargain: we like it for its wealth production and efficiency, but at bottom it is really about greed. It is rapacious and immoral.
>- It is readily apparent that many of our colleagues in the business disciplines believe this notion
>- __I'm afraid that our students do too!__ They leave the business school with some good technical tools, but not with an appreciation of just how much good they will do in their careers. 
>- That is on us! That's a failure on our part to teach correct principles.

@@

## A Simple Dutch Book Example

- Consider Agent A's degrees of belief regarding the flipping of a fair coin.

- The event space is $S = \{H,T \}$ $\quad \quad$ ($H = \mbox{"heads"}$, and $T = \mbox{"tails"}$)

- Suppose A's beliefs can be represented as $P(H) = 0.51$ and $P(T) = 0.51$

- That is, A will pay $\$0.51$ to receive $\$1$ in the event of a "heads", and simultaneously will pay $\$0.51$ to receive $\$1$ in event of a "tails".

- Now, either a "heads" or "tails" will occur, so A is guaranteed to earn $\$1$ regardless of the state of the world that results

- But A's bets total $\$1.02$, so A is guaranteed to lose $\$0.02$ regardless of the state of the world that results.

- A Dutch book has been made against A!

@@

<center>
<img src="images/xkcd.png" width=600 height=550 />
</center>
